Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-04-14 paper/paper.tex
Fix references again

% \newcommand{\texten}[1]{}
% \newcommand{\textru}[1]{\foreignlanguage{russian}{\emph{#1}}{}}

\newcommand{\texten}[1]{#1}
\newcommand{\textru}[1]{\\
  \foreignlanguage{russian}{\emph{#1}}}

@@

The norm and modulus of the gradient are metrical characteristic of a function of
two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod\cite{mak2}
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a number
of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

For memory-tight applications such as embedded systems it can be useful to
utilise the suggested condensation in a lazy way, so that without actually
constructing the condensed image we use a function (``view'') calculating color of
each cell with 4 lookups to the original binary image.
This is probably most interesting when combined with SUF2 algorithm, as it is a way
to win some time while avoiding memory footprint increase.
However this lazy approach increases the number of image lookups.
% So, according to our benchmark, this combination is efficient only for dense
% ($>30\%$) noise.

@@

The test images were generated in the following manner. At first, 
for given density $d$, the first $4dNM$ pixels of
the $2N \times 2M$ image were filled with object values, while rest filled with background values.
Then all the pixels were permuted using \texttt{std::shuffle} function from \CXX standard library,
which is an implementation of Fisher-Yates Shuffle algorithm\cite{fisher:yates}.

@@

Line charts with benchmarks of mentioned algorithms on different noise images are shown on
\Cref{fig:noise400x600,fig:noise800x1200,fig:noise1200x1800,fig:noise2000x3000,fig:noise4000x6000}.

@@

\newcommand{\inputtable}[2]{
  \begin{figure}
    \centering
    \includegraphics[height=0.45\textheight, keepaspectratio]{pics/#1x#2.eps}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px.}
    \label{fig:noise#1x#2}
  \end{figure}
 % \begin{table}[p]
 %   \centering
 %   \input{tables/#1x#2}
 %   \caption{Average CPU time per run on noise images $#1 \times #2$ px}
 %   \label{tab:noise#1x#2}
 % \end{table}
}

% \inputtable{200}{300}
\inputtable{400}{600}
\inputtable{800}{1200}
\inputtable{1200}{1800}
\inputtable{2000}{3000}
\inputtable{4000}{6000}
% \inputtable{5000}{7500}

@@

\bibitem {mak2}
Kronrod, A.: On functions of two variables ," Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

@@

\bibitem {mak4}
4.	Makovetskii, A., Kober, V.: Modified gradient descent method for image restoration. Proc. SPIE Applications of Digital Image Processing XXXVI, 8856, 885608-1 (2013)

@@

\bibitem {CLRS}
Cormen, H., Leiserson, E., Rivest, L., Stein, C.:
Introduction to Algorithms (Second ed.), MIT Press (2001)

@@

\bibitem {fisher:yates}
 Fisher, A., Yates, F.:
 Statistical tables for biological, agricultural and medical research (3rd ed.). 
 London: Oliver \& Boyd. pp. 26–27. OCLC 14222135 (1948)

\bibitem{mt19937}
Matsumoto, M., Nishimura, T.:
"Mersenne twister: a 623-dimensionally equidistributed uniform pseudo-random number generator".
ACM Transactions on Modeling and Computer Simulation 8 (1): 3–30. (1998)

>>>>

\newcommand{\texten}[1]{#1}
\newcommand{\textru}[1]{}

%% Чтобы переключиться на русский язык в некоторых секциях, можно 
%% раскомментировать следующие две команды
% \renewcommand{\texten}[1]{}
% \renewcommand{\textru}[1]{\foreignlanguage{russian}{\emph{#1}}{}}

%% Чтобы оставить оба языка, можно раскомментировать
%% следующие две команды
% \renewcommand{\texten}[1]{#1}
% \renewcommand{\textru}[1]{\\ \foreignlanguage{russian}{\emph{#1}}}

@@

The norm and modulus of the gradient are metrical characteristic of a function of
two variables.
Continuous functions of two variables also have a set of topological
characteristics referred to as linear variations.
Kronrod%\cite{mak2}
introduced the notion of a regular component of the level set of a
continuous function of two variables.
The simplest topological characteristic in the linear variation theory is a number
of regular components for all level sets of a function.
Full information about linear variations of a function is contained in the
one-dimensional tree of a function of two variables.
In \cite{mak3,mak4,mak5}
was discussed the necessity of the using a linear variation in the
image restoration theory.

@@

\texten{
For memory-tight applications such as embedded systems it can be useful to
utilise the suggested condensation in a lazy way, so that without actually
constructing the condensed image we use a function (``view'') calculating color of
each cell with 4 lookups to the original binary image.
This is probably most interesting when combined with SUF2 algorithm, as it is a way
to win some time while avoiding memory footprint increase.
However this lazy approach increases the number of image lookups.
% So, according to our benchmark, this combination is efficient only for dense
% ($>30\%$) noise.
}\textru{
В некоторых случаях может быть более приемлемо использовать сжатие неявно, то
есть вместо построения 
}

@@

The test images were generated in the following manner. At first, for given
density $d$, the first $4dNM$ pixels of the $2N \times 2M$ image were filled
with object values, while rest filled with background values. Then all the
pixels were permuted using \texttt{std::shuffle} function from \CXX standard
library, which is an implementation of Fisher-Yates Shuffle
algorithm%\cite{fisher:yates}
.

@@

Line charts with benchmarks of mentioned algorithms on different noise images
are shown on
\Cref{fig:overall:times}.

@@

\begin{figure}
  \centering
  \includegraphics[height=0.45\textheight, keepaspectratio]{pics/overall.eps}
  \caption{Average CPU time per run on random images $1200 \times 1800$ px.}
  \label{fig:overall:times}
\end{figure}

\newcommand{\inputnorm}[1]{
  \begin{subfigure}[t]{0.45\linewidth}
    \centering
    \includegraphics[width=\textwidth,
                     keepaspectratio]{pics/normed_#1.eps}
    \caption{Some.}
    \label{fig:normed:#1}
  \end{subfigure}
}

\begin{figure}
  \centering
  \inputnorm{DFS}
  \inputnorm{SUF}
  \inputnorm{SUF2}
  \inputnorm{DTSUF}
  \label{fig:normed}
\end{figure}

@@

% \bibitem {mak2}
% Kronrod, A.:
% On functions of two variables.
% Uspehi Mat. Nauk 5, 1(35), 24-134(1950)

@@

\bibitem {mak4}
Makovetskii, A., Kober, V.:
Modified gradient descent method for image restoration.
Proc. SPIE Applications of Digital Image Processing XXXVI, 8856, 885608-1 (2013)

@@

\bibitem {CLRS}
Cormen, H., Leiserson, E., Rivest, L., Stein, C.:
Introduction to Algorithms (Second ed.).
MIT Press (2001)

@@

% \bibitem {fisher:yates}
% Fisher, A., Yates, F.:
% Statistical tables for biological, agricultural and medical research (3rd ed.).
% London: Oliver \& Boyd. pp. 26–27. OCLC 14222135 (1948)

\bibitem{mt19937}
Matsumoto, M., Nishimura, T.:
Mersenne twister: a 623-dimensionally equidistributed uniform pseudo-random
number generator.
ACM Transactions on Modeling and Computer Simulation 8 (1): 3–30. (1998)
